Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-04-21 paper.tex
Added files via upload

To pursue these three possibilities further, we employ cosmological
simulations of CRs in clusters. In tandem with new insights from our
recent work on DSA generated fossil electrons \citep{pinzke13}, we
generate the first quantitative calculation of primary and secondary
seed electrons and compare to observations in the Coma cluster. For
the most part, we adopt parameters that are used in previous work: for
details, see \citep[][ turbulent spectrum]{brunetti07,brunetti11},
\citep[][ injection scale of turbulens]{2015ApJ...800...60M},
\citep[][ energy density of
  turbulence]{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
for CR acceleration in shocks, \citep[][ in particular $K_{\rmn{ep}}$,
  acceleration efficiency]{pinzke13}, and for cosmological
simulations, \citep[][ i.e., shock history, temperature profile,
  density profile, magnetic field profile]{pinzke10}. All these
parameters are uncertain, and could potentially change our
predictions. We refere the reader to section~\ref{sect:param_comp} for
a small exploration of parameter space, however we leave the full
exploration of parameter space and the interaction between free
parameters to future work.

@@

\subsection{Turbulent reacceleration}

We incorporate momentum diffusion for electrons and protons from
transit-time-damping (TTD) resonance with compressible MHD turbulence,
to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
TTD resonance requires the wave frequency
$\omega=k_\parallel\upsilon_\parallel$, where $k_\parallel$ and
$\upsilon_\parallel$ are the parallel (projected along the magnetic
field) wavenumber and particle velocity, respectively. This implies
that the particle transit time across the confining wave region
matches the wave period, $\lambda_{\parallel}/v_{\parallel}=T$. Note,
the CRs' gyroradius does not enter the resonance condition. Hence the
CRs that are in resonance with compressible waves experience Fermi-II
acceleration irrespectively of the length scale of the perturbation.

@@

  beter? why not 1 Mpc}

@@

\Mprimary (see Figure~\ref{fig:turb} for visualisation). Note that in

@@

\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
\hline
thermal quantities$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
timescales$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
$\tau_\rmn{had}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a.\\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\

 \label{tab:timescales}
  \end{quote}
\end{table}

\subsection{Scaling relations for turbulent reacceleratio}
The diffusion constant, $D_\rmn{pp}\propto I_0/\rho c_s \propto
X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}$, where
we adopt the same level of compressible turbulence, $X_\rmn{tu}=0.2$,
for all models. The reaccelerated CRs are exponentially dependent on
this parameter as long as $\tau_D > \tau_\rmn{cl}$, where
$\tau_\rmn{cl}$ represent the duration of reacceleration of the merger
which we assume to be 650~Myrs long. Note that a fixed reacceleration
timescale $\tau_D\sim 1/D_\rmn{pp}\sim 0.2-0.7\,\rmn{Gyr}$ is required
to explain the observations for each model and radial bin (see
Table~\ref{tab:timescales}). This allows us to interchange
$\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$, i.e. a longer
reacceleration duration have to be compensated by lowering the level
of turbulence or increasing the physical injection scale of turbulence
to keep $\tau_D$ constant.

\subsection{Spherically symmetric models}
In this section we develope a simple framework that will be used to
test the robustness of our models to the critical parameters for CRs
and turbulence in section~\ref{sect:param_comp}. Here we do not follow
single Lagrangian particles in the cluster, instead we use a more
simple approach where we solve the Fokker-Plack equation in static
spherical shells for injection, reacceleration, and losses of the
CRs. Once the CRs have been reaccelerated for $\tau_\rmn{cl} =
650\,\rmn{Myr}$, we calculate the radio emission and compare the
profile and spectra for different parametrizations.

We adopt both the density \cite{1992A&A...259L..31B} and temperature
\cite{2009ApJ...696.1886B,2001A&A...365L..67A} profiles derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/294\,\rmn{kpc}\right)^2\right]^{1.125}}\nonumber\\
T k_B &=& 8.25\,\rmn{keV} \left[1+\left(R/0.5R_{200}\right)^2\right]^{-0.32}\,.
\end{eqnarray}
The virial radius of Coma is given by $R_{200} = 2300\,\rmn{kpc}$.
The bulk of the CRps are injected by relatively low Mach number shocks
and parametrized by $f_\rmn{CRp,inj}(p) =
C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
where the normalization is fixed by assuming that the injected CR
energy in the last 650~Myrs make up 0.03\% of the thermal energy
inside the virial radius, i.e.
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V = 0.0003$. The spectrum of
  the initial CRp distibtion is determined by the steady state between
  injection and cooling,
\begin{equation}
 f_{CRp,0} \approx \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
\rmn{d}p'}{\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where the normalization is fixed by
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj}
\rmn{d}V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V =
0.003$. Similarly, the initial CRe distribution is given by the steady
state between cooling (Coulomb, invers Compton, and synchroton) and
injection of secondary CRes from $f_{CRp,0}$. We also include the
contineous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reacceleating both the CRps
and CRes is parametrized by $I_0 \propto X_\rmn{tu} (n_e
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

@@

% --- section: Analytical Results and discussion --- %
\section{Parameter space exploration with spherical models}
\label{sect:param_comp}
in this paper we rely on several critical parameters decribing
relatively unknown non-thermal physics in the ICM. Here we try to
explore the robustness of our models to the most critical parameters
related to turbulence and CRs. Figure~\ref{fig:param_comp} shows their
impact on radio emission. We find that the level of turbulence
($X_\rmn{tu}$) has a large impact on both radio spectra and profile,
while the parameter $\alpha_\rmn{tu}$ that determines the spatial
profile of turbulence mainly influence the radio profiles. As
expected, the radio profiles flatten significantely with a flatter
turbulent profile. A higher amount of energy also flatten the radio
profile, where the reason beeing that the steep profiles of injected
CRs have less impact on the radio emission for an increasing
reacceleration efficiency. Interestingly, assumptions about CRs have
less impact on radio emission. This can be understood by looking at
the scaling of parameters to the reacceleration timescale, where
$\tau_\rmn{D} \propto X_\rmn{tu}^2$. The CRps approximately gain a
factor $\Delta C_\rmn{reacc.} \sim
\exp{\left[\frac{(2+\alpha)(1-\alpha)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}$
during reacceleration if injection and cooling are neglected. The CRes
gain a similar factor from reacceleration, however in the region
around $0.1\,R_{200}$ the Coulomb cooling timescale
($\tau_\rmn{coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
$\tau_\rmn{D}\approx0.5\,\rmn{Gyr}$, hence $\Delta C_\rmn{reacc.}$
will be greatly reduced for the electrons. The spatial region is
important when we derive the radio spectrum, since in order to compare
to observations we integrate the CR profile out to $\sim
0.2\,R_{200}$. For a CRp spectral index $\alpha_\rmn{CR}\sim 2.5$,
$\Delta C_\rmn{reacc.} \sim
\exp{\left[1.7\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]} \sim 10$ for
$X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$. This is confirmed by the
top panels in Fig.~\ref{fig:param_comp}. Increasing the level of
turbulence to $X_\rmn{tu}=0.3$, gives us a $\Delta C_\rmn{reacc.}
\sim 100$, which is roughly confirmed by same figures. The factor 2-3
difference in the figure is due to the shorter reacceleration
timescale that increase the contribution from reaccelerated CRes that
would othervise cool away on a much shorter timescale. Hence we
conclude that the radio emission is much more sensitive to the
exponential dependence on compressible turbulence than the linjear
dependence on injected CRs. \AP{Too complicated? Perhaps cut or
  simplify?}

We can also find a lower critical level of turbulence where
reacceleration is negliable, while it rises sharply above this
threshold. We define the threshold by $\Delta C_\rmn{reacc.}  \lesssim
2$, which gives us an $X_\rmn{thres,tu} = \left(\frac{\log(2)
  0.04}{1.7}\frac{\tau_\rmn{D}}{\tau_\rmn{cl}}\right)^{0.5} \approx 0.08$ for
$\tau_\rmn{D} = 0.5\,\rmn{Myr}$. This threshold is also seen in the
top panels of figure~\ref{fig:param_comp}. For instance, for
$X_\rmn{tu}\gtrsim0.08$, a factor two change in $X_\rmn{tu}$ changes
the radio surface brightness by a factor $\sim 10-100$. In principle
this threshold behavior allows us to provide a strict lower bound on
turbulence in radio halos. An even more stringent bound on
$X_\rmn{tu}$ can be inferred from combining radio observations with
the gamma-ray observations (see section~\ref{sect:radio_spec}).

>>>>

To pursue these three possibilities further, we employ cosmological
simulations of CRs in clusters. In tandem with new insights from our
recent work on DSA generated fossil electrons \citep{pinzke13}, we
generate the first quantitative calculation of primary and secondary
seed electrons and compare to observations in the Coma cluster. For
the most part, we adopt parameters that are used in previous work: for
details, see \citep[][ turbulent spectrum]{brunetti07,brunetti11},
\citep[][ injection scale of turbulens]{2015ApJ...800...60M},
\citep[][ energy density of
  turbulence]{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
for CR acceleration in shocks, \citep[][ in particular $K_{\rmn{ep}}$,
  acceleration efficiency]{pinzke13}, and for cosmological
simulations, \citep[][ i.e., shock history, temperature profile,
  density profile, magnetic field profile]{pinzke10}. All these
parameters are uncertain, and could potentially change our
predictions. We refer the reader to section~\ref{sect:param_comp} for
a minor exploration of parameter space, and leave the full exploration
of parameter space and the interaction between free parameters to
future work.

@@

\subsection{Turbulent reacceleration}
We incorporate momentum diffusion for electrons and protons from
transit-time-damping (TTD) resonance with compressible MHD turbulence,
to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
TTD resonance requires the wave frequency
$\omega=k_\parallel\upsilon_\parallel$, where $k_\parallel$ and
$\upsilon_\parallel$ are the parallel (projected along the magnetic
field) wavenumber and particle velocity, respectively. This implies
that the particle transit time across the confining wave region
matches the wave period, $\lambda_{\parallel}/v_{\parallel}=T$. Note,
the CRs' gyroradius does not enter the resonance condition. Hence the
CRs that are in resonance with compressible waves experience Fermi-II
acceleration irrespectively of the length scale of the perturbation.

@@

  better? why not 1 Mpc}

@@

\Mprimary (see Figure~\ref{fig:turb} for visualization). Note that in

@@

\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
\hline
thermal quantities$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
timescales$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
$\tau_\rmn{had}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a.\\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\
 \label{tab:timescales}
  \end{quote}
\end{table}

\subsection{Scaling relations for turbulent reacceleration}
To understand the radial dependence of the diffusion constant we
investigate how $D_\rmn{pp}$ scales with different parameters. This is
crucial in order to identify important parameters, and understand the
profile of reaccelerated CRs and radio emission. Combining
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e} we find that $D_\rmn{pp}\propto
I_0/\rho c_s \propto
X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}$. Here we
immediately see that if the turbulent profile trace the thermal energy
(i.e. $\alpha_\rmn{tu}=1$), the square root of temperature alone
determines the diffusion constant. We also see that $D_\rmn{pp}$ is
much more sensitive to $X_\rmn{tu}$ than $k_0$.

During reacceleration the CRps approximately gain a factor 
\begin{equation}
  \label{eq:Creacc}
  \Delta C_\rmn{reacc.} \sim
  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
\end{equation}
if injection and cooling are neglected. The reaccelerated CRs are then
exponentially dependent on $D_\rmn{pp}$ as long as $\tau_D \lesssim
\tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
reacceleration of the merger which we assume to be 650~Myrs long.
Note that a fixed reacceleration timescale $\tau_D\sim
1/D_\rmn{pp}\sim 0.2-0.7\,\rmn{Gyr}$ is required to explain the
observations at each radius and for each model (see
Table~\ref{tab:timescales}). This allows us to interchange
$\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$, i.e. a longer
reacceleration duration have to be compensated by lowering the level
of turbulence or increasing the physical injection scale of turbulence
to keep $\tau_D$ constant.

\subsection{Spherically symmetric models}
In this section we develop a simple framework that will be used to
test the robustness of our models to the critical parameters for CRs
and turbulence in section~\ref{sect:param_comp}. Here we do not follow
single Lagrangian particles in the cluster, instead we use a more
simple approach where we solve the Fokker-Planck equation in static
spherical shells for injection, reacceleration, and losses of the
CRs. Once the CRs have been reaccelerated for $\tau_\rmn{cl} =
650\,\rmn{Myr}$, we calculate the radio emission and compare the
profile and spectra for different parameterizations.

We adopt both the density \cite{1992A&A...259L..31B} and temperature
\cite{2009ApJ...696.1886B,2001A&A...365L..67A} profiles derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/294\,\rmn{kpc}\right)^2\right]^{1.125}}\nonumber\\
T k_B &=& 8.25\,\rmn{keV} \left[1+\left(R/0.5R_{200}\right)^2\right]^{-0.32}\,.
\end{eqnarray}
The virial radius of Coma is given by $R_{200} = 2300\,\rmn{kpc}$.
The bulk of the CRps are injected by relatively low Mach number shocks
and parameterized by $f_\rmn{CRp,inj}(p) =
C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
where the normalization is fixed by assuming that the injected CR
energy in the last 650~Myrs make up 0.03\% of the thermal energy
inside the virial radius, i.e.
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V = 0.0003$. The spectrum of
  the initial CRp distribution is determined by the steady state between
  injection and cooling,
\begin{equation}
 f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
\rmn{d}p'}{\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where the normalization is fixed by
$\int_0^{R_{200}}\epsilon_\rmn{CRp,0}
\rmn{d}V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V =
0.003$. Similarly, the initial CRe distribution is given by the steady
state between cooling (Coulomb, inverse Compton, and synchrotron) and
injection of secondary CRes from $f_{CRp,0}$. We also include the
continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reaccelerating both the CRps
and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_e
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

@@

% --- section: Analytical Results and discussion --- %
\section{Parameter space exploration with spherical models}
\label{sect:param_comp}
In this paper we rely on several critical parameters describing
relatively unknown non-thermal physics in the ICM. Here we try to
explore the robustness of our models to the most critical parameters
related to turbulence and CRs. Figure~\ref{fig:param_comp} shows their
impact on radio emission. We find that the level of turbulence
($X_\rmn{tu}$) has a large impact on both radio spectra and profiles,
while the parameter $\alpha_\rmn{tu}$ that determines the spatial
profile of turbulence mainly influence the radio profiles. As
expected, the radio profiles flatten significantly with a flatter
turbulent profile. A higher amount of turbulent energy also flatten
the radio profile, where the reason being that the steep profiles of
injected CRs have less impact on the radio emission for an increasing
reacceleration efficiency. Interestingly, assumptions about CRs have
less impact on radio emission. This can be understood by looking at
the scaling of parameters to the reacceleration timescale, where
$\tau_\rmn{D} \propto 1/D_\rmn{pp} \propto 1/X_\rmn{tu}^2$. From
Eqn.~\ref{eq:Creacc} we see that the CRps with a spectral index of
$\alpha_\rmn{CR}\approx2.5$ approximately gain a factor $\Delta
C_\rmn{reacc.} \sim
\exp{\left[1.7\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}$ during
reacceleration if injection and cooling are neglected. The CRes gain a
similar factor from reacceleration, however in the region around
$0.1\,R_{200}$ the Coulomb cooling timescale
($\tau_\rmn{coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
$\tau_\rmn{D}\approx0.5\,\rmn{Gyr}$, hence $\Delta C_\rmn{reacc.}$
will be greatly reduced for the electrons. The spatial region is
important when we derive the radio spectrum, since in order to compare
to observations we integrate the CR profile out to $\sim
0.2\,R_{200}$. For $X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$ we find
that $\Delta C_\rmn{reacc.} \sim 10$. This is confirmed by the top
panels in Fig.~\ref{fig:param_comp}. Increasing the level of
turbulence to $X_\rmn{tu}=0.3$, gives us a $\Delta C_\rmn{reacc.}
\sim 100$, which is roughly confirmed by same figures. The factor 2-3
difference in the figure is due to the shorter reacceleration
timescale that increase the contribution from reaccelerated CRes that
would otherwise cool away on a much shorter timescale. Hence we
conclude that the radio emission is much more sensitive to the
exponential dependence on compressible turbulence than the linear
dependence on injected CRs.

We can also derive a lower critical level of turbulence where
reacceleration is negligible, while it rises sharply above this
threshold. We define the threshold by $\Delta C_\rmn{reacc.}  \lesssim
2$, which gives us an $X_\rmn{thres,tu} = \left(\frac{0.04\,\log(2)
}{1.7}\frac{\tau_\rmn{D}}{\tau_\rmn{cl}}\right)^{0.5} \approx 0.08$
for $\tau_\rmn{D} = 0.5\,\rmn{Myr}$. This threshold is also seen in
the top panels of figure~\ref{fig:param_comp}. For instance, for
$X_\rmn{tu}\gtrsim0.08$, a factor two change in $X_\rmn{tu}$ changes
the radio surface brightness by a factor $\sim 10-100$. In principle
this threshold behavior allows us to provide a strict lower bound on
turbulence in radio halos. An even more stringent bound on
$X_\rmn{tu}$ can be inferred from combining radio observations with
the gamma-ray observations (see section~\ref{sect:radio_spec}).
